---
title: "Examples"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
library(lubridate)
library(stringr)
source("oranks.R")
```
### Ostats Example Usage  

Available Functions:  
* `o_rank_course()`  
* `o_runner_results()`  
* `o_courses()`  
* `o_events()`  
* `o_clubs()`  

### Course Rankings:  

The `o_rank_course()` function is used to access the combined rankings for a given course and date.  

#### Red Runners by Current Course Rank:  
```{r}
red <- o_rank_course(course = "red", rank_date = "current") %>%
  arrange(Overall_Rank, -Count_Events, -Score)
print(red, n = 10, width = Inf)
```

#### F-20 Rankings for 2014:  
```{r}
F20 <- o_rank_course("green", "2014-12-31") %>%
  filter(Class == "F-20") %>%
  arrange(Class_Rank, -Count_Events, -Score)
print(F20, n = 10, width = Inf)
```

### Runner's Results  

The `o_runner_results()` function is used to access the complete course history of courses used in national rankings.  

```{r}
results <- suppressMessages(o_runner_results("culberg", "kevin"))
ggplot(filter(results, Score > 0), aes(x = Date, y = Score)) +
  geom_smooth(se = FALSE) +
  geom_point(aes(color = Class)) +
  coord_cartesian(ylim = c(0, 100))
```

### Course Data  

The `o_courses()` function is used to access the course stats including date, length, controls and CGV.  
```{r}
courses <- o_courses()
print(courses, n = 10, width = Inf)
```

#### Number of Controls on All Blue Courses by Year:

```{r}
controls <- courses %>%
  filter(Course == "Blue") %>%
  group_by(Year = year(Date)) %>%
  summarise(`Total Controls` = sum(Ctrls))
ggplot(controls, aes(x = Year, y = `Total Controls`)) +
  geom_bar(stat = "identity")
```

### Event Data  

The `o_events()` function is used to access event information including name, date and club.  

#### Orienteering Season:  
```{r}
events <- o_events() %>%
  group_by(Month = month(Date), Year = year(Date)) %>%
  summarise(Count = n()) %>%
  summarise(`Avg Events` = sum(Count)/7)
ggplot(events, aes(x = factor(Month, levels = 1:12), y = `Avg Events`)) +
  geom_bar(stat = "identity") +
  scale_x_discrete(name = "Month", labels = month.abb)
```

### Club Data  