---
title: "O-Rank Research"
output: html_notebook
---

```{r include = FALSE}
library(tidyverse)
library(rvest)
library(lubridate)
source("oranks.R")
```


What is CGV for courses?

### Variables:
* runners: score, age, # events, course/class, years orienteering, club
* clubs: # events, # competitors
* events: type, distance, controls, climb, date, cgv

### Questions:
* How does an orienteer's rank change over time?
* Are clubs hosting more or less national level meets?
* When was the golden age of orienteering competitors?
* When was the golded age of orienteering events?
* How does an orienteer's age and experience correlate to their score?
* Which club is the best? (best elite competitors)
* Which club has the best depth of competitors?

### Top Blue Runners:
```{r}
blue <- o_rank_course(rank_date = "2016-10-31", course = "blue")
print(blue, n = 10)
```

### Blue Runners Score vs # of Events:
```{r}
ggplot(blue, aes(x = Score, y = Count_Events)) + geom_point()
```

### Kevin Culberg's Results
```{r}
results <- suppressMessages(o_runner_results("culberg", "kevin"))
print(results, n = 10)
ggplot(filter(results, Score > 0), aes(x = mdy(Date), y = Score)) + geom_point(aes(color = Course)) + geom_smooth() + coord_cartesian(ylim = c(0, 100))
```


