---
title: "Ostats Research"
output: html_notebook
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
library(lubridate)
library(stringr)
source("oranks.R")
```

### Variables:
* runners: score, age, # events, course/class, years orienteering, club
* clubs: # events, # competitors
* events: type, distance, controls, climb, date, cgv

### Questions:
* How does an orienteer's rank change over time?
* Are clubs hosting more or less national level meets
* When was the golden age of orienteering competitors
* When was the golded age of orienteering events?
* How does an orienteer's age and experience correlate to their score?

### Other:
* What is CGV for courses? course gnarliness value - probably calculated using top3 pace, distance, climb

### Which club is the best?

Source data is current year's rankings for advanced courses (blue, red, green)
Group by class (M-21+, F-21+, etc.)
x axis is each club, y axis is the score

```{r, fig.align="center"}
cur.blue <- o_rank_course("blue")
cur.M21 <- cur.blue %>% 
  filter(Count_Events > 3, Club != "")
ggplot(cur.M21) +
  ggtitle("M-21+ Scores by Club") +
  geom_boxplot(aes(x = Club, y = Score), fill = "#72a8ff") +
  scale_y_continuous(breaks = seq(0, 140, 10)) +
  coord_flip() + theme_linedraw()
```
```{r, fig.align="center"}
cur.red <- o_rank_course("red")
cur.F21 <- cur.red %>%
  filter(Count_Events > 3, Club != "", Class == "F-21+")
ggplot(cur.F21) +
  ggtitle("F-21+ Scores by Club") +
  geom_boxplot(aes(x = Club, y = Score), fill = "#ff3a3a") +
  scale_y_continuous(breaks = seq(0, 140, 10)) +
  coord_flip() + theme_linedraw()
```
```{r, fig.align="center", fig.height = 8}
cur.green <- o_rank_course("green")
cur.adv <- bind_rows(cur.blue, cur.red, cur.green) %>%
  filter(Count_Events > 3, Club != "")
ggplot(cur.adv) + 
  ggtitle("Advanced Course Scores by Club") +
  geom_boxplot(aes(x = Club, y = Score), fill = "#f76d22") +
  scale_y_continuous(breaks = seq(0, 140, 10)) +
  coord_flip() + theme_linedraw()
```

Source data is events to identify which club is hosting the most events

```{r, fig.align="center", fig.height = 6}
club.events <- o_events() %>%
  group_by(Club) %>%
  summarise(Count = n())
ggplot(club.events, aes(x = reorder(Club, -Count), y = Count)) + 
  ggtitle("Number of Events Hosted by Clubs Since 2010") +
  geom_bar(stat = "identity", fill = "#6FBF40", color = "black") +
  scale_y_continuous(breaks = seq(0, 30, 5), name = "Number of Events") +
  coord_flip() + theme_linedraw() + xlab("Club")
```

